A Theory for Data Migration of Information Systems

### 2022-09-17 2022 Migration/articleMigration.tex
WIP

\section{Introduction}
\label{sct:Introduction}
	Data migration occurs when one stateful information system, $\infsys$, is replaced by another, $\infsys'$,
	while the data from $\infsys$ must be preserved.
	Agile teams today need to automate their data migrations, 
	as they do for all other activities in their software process.
	By continually automating their own work,
	teams keep improving their DevOps metrics such as deployment frequency, reliability of deployments, and change failure rate~\cite{DevOps2021}.

>>>>

\section{Introduction}
\label{sct:Introduction}
	Data migration occurs when one stateful information system, $\infsys$, is replaced by another, $\infsys'$,
	while the data from $\infsys$ must be preserved.
	Agile teams today need to automate their data migrations, 
	as they do for all other activities in their software process.
	Teams continually automate to keep improving their performance without working any harder.
	They measure the effects in terms of DevOps metrics such as
	deployment frequency,
	reliability of deployments, and
	change failure rate~\cite{DevOps2021}.
